Asimilación de distintas observaciones

### 2020-12-04 analysis/chapters/experimento_20181122.Rmd
Muchas figuras nuevas

@@

}) %>% 
  rbindlist() %>% 
  .[, date := ymd_hms(date)] %>% 
  .[date %between% c(as_datetime("2018-11-20 18:00:00"),
                     as_datetime("2018-11-23 12:00:00"))]

perfiles %>% 
  dcast(lev + date ~ exp, value.var = "T") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value), breaks = seq(-1, 1, 0.2)) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-1, 1, 0.2),
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Temperature difference (K)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r Q-diff, fig.cap="Specific humidity difference between experiments in g/Kg"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "QVAPOR") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E5)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value*1000), breaks = seq(-0.0016, 0.0016, 0.0002)*1000) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-0.0016, 0.0016, 0.0002)*1000,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +

@@

The differences between RAD and SATWND and therefore the impact of the radiances have opposite sign to the impact of the observations from automatic stations but with smaller magnituded in low levels. A positive difference can also be observed between 850 and 600 hPa.

```{r U-diff, fig.cap="Zonal wind difference between experiments in m/s (filled contours) and zonal wind profile for the experiment with more observations."}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value), breaks = seq(-1.2, 1.4, 0.2)) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-1.2, 1.4, 0.2),
                       labels = function(x) round(x, digits = 1),
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(0, 30, 3), size = 0.3, linetype = 1, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(0, 30, 3), color = "grey30", skip = 1, stroke = 0.2) +
  labs(subtitle = "U difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value), breaks = seq(-1.8, 1.2, 0.2)) +
  scale_fill_divergent(name = NULL,
                       breaks = seq(-1.8, 1.2, 0.2),
                       labels = function(x) round(x, digits = 1),
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(-7, 0, 1), size = 0.3, linetype = 2, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(-7, 0, 1), color = "grey30", skip = 1, stroke = 0.2) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

```{r q-wind, warning=FALSE, fig.align="center", message=FALSE,dev="png"}
fcsts <- expand_grid(fcsts = c("20181121180000", "20181122000000", "20181122060000"),
                     exp = c("E4", "E5", "E6", "E7"))

@@

q[bottom_top %between% c(0, 7), .(q = mean(q), u = u[bottom_top == 1], v = v[bottom_top == 1]), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = q*1000, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 0.02, 0.002)*1000) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       limits = c(1, 19),
                       guide = guide_colorsteps(#inside = FALSE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  # geom_vector(aes(x = lon, y = lat,
  #                 dx = u, dy = v), data = function(x) x[is.cross(y, x, 8)],
  #             arrow.angle = 12, size = 0.3) +
  # scale_mag() +
  cordillera +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Low level humidity (g/Kg)",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```
```{r}

q[bottom_top %between% c(8, 12), .(q = mean(q), u = u[bottom_top == 1], v = v[bottom_top == 1]), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = q*1000, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 0.02, 0.002)*1000) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       limits = c(1, 19),
                       guide = guide_colorsteps(#inside = FALSE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  # geom_vector(aes(x = lon, y = lat,
  #                 dx = u, dy = v), data = function(x) x[is.cross(y, x, 8)],
  #             arrow.angle = 12, size = 0.3) +
  # scale_mag() +
  cordillera +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Humidity (g/Kg) 800-700 hPa",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

>>>>

```{r rad}

files <- Sys.glob("/home/paola.corrales/datosmunin/EXP/E7/ANA/*/diagfiles/asim*ensmean")

files <- files[!str_detect(files, "conv")]

rad <- read_diag_rad(files, "E7")

satinfo <- fread(here("analysis", "data", "derived_data", "satinfo.txt")) %>% 
  setnames(c("!sensor/instr/sat", "chan"), c("sensor", "channel"))

rad <- satinfo[rad, on = c("sensor", "channel")]

rad %>% 
  .[qc == 0 & iuse == 1] %>% 
  .[, lev := cut_width(peakwt, 50)] %>% 
  .[, .(omb = mean(tbc),
              n = .N), by = .(date, lev)] %>% 
  ggplot(aes(date, fct_rev(lev))) +
  geom_raster(aes(fill = omb)) +
  scale_fill_divergent(trans = mesoda::symlog_trans(),
                       guide = guide_colourbar(barheight = 20))  +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H:%M") +
  labs(x = NULL, fill = NULL, y = "pressure layer")

rad %>% 
  .[qc == 0 & iuse == 1] %>% 
  .[, lev := cut_width(peakwt, 50)] %>% 
  .[, .(omb = mean(tbc),
              n = .N), by = .(date, lev)] %>% 
  ggplot(aes(date, fct_rev(lev))) +
  geom_raster(aes(fill = n)) +
  scale_fill_viridis_c(trans = scales::log10_trans(),
                       guide = guide_colourbar(barheight = 20)) +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H:%M") +
  labs(x = NULL, fill = NULL, y = "pressure layer")

@@

}) %>% 
  rbindlist() %>% 
  .[, date := as_datetime(date)] %>% 
  .[date %between% c(as_datetime("2018-11-20 18:00:00"),
                     as_datetime("2018-11-23 12:00:00"))]

perfiles %>% 
  dcast(lev + date ~ exp, value.var = "T") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level))) +
  scale_fill_divergent_discretised(name = NULL,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Temperature difference (K)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r T-mse, fig.cap="MSE Temperature between analysis and guess in Kelvin^2."}

files <- Sys.glob("/home/paola.corrales/datosmunin/EXP/derived_data/perfiles_mse*")

perfiles_mse <- purrr::map(files, function(f) {
  exp <- unglue(basename(f), "perfiles_{run}_{exp}.csv")
  fread(f) %>% 
    .[, run := exp[[1]][["run"]]] %>% 
    .[, exp := exp[[1]][["exp"]]]

}) %>% 
  rbindlist() %>% 
  .[, date := as_datetime(date)] %>% 
  .[date %between% c(as_datetime("2018-11-20 20:00:00"),
                     as_datetime("2018-11-23 12:00:00"))]

perfiles_mse %>% 
  .[variable == "T"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = mse, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Temperature MSE (K^2)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r Q-diff, fig.cap="Specific humidity difference between experiments in g/Kg"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "QVAPOR") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E5)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value*1000, fill = stat(level)), 
                    breaks = c(seq(-1, 1.6, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL, limits = c(-1, 1.6),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +

@@

The differences between RAD and SATWND and therefore the impact of the radiances have opposite sign to the impact of the observations from automatic stations but with smaller magnituded in low levels. A positive difference can also be observed between 850 and 600 hPa. 
```{r Q-mse, fig.cap="MSE Specific humidity between analysis and guess in g/Kg^2."}

perfiles_mse %>% 
  .[variable == "QVAPOR"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = mse*1000000, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Specific humidity MSE (g/Kg^2)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r U-diff, fig.cap="Zonal wind difference between experiments in m/s (filled contours) and zonal wind profile for the experiment with more observations."}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), breaks = c(seq(-1.6, 2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL,
                       limits = c(-1.6, 2),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(0, 30, 3), size = 0.3, linetype = 1, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(0, 30, 3), color = "grey30", skip = 1, stroke = 0.2) +
  labs(subtitle = "U difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), 
                    breaks = c(-Inf, seq(-1.6, 1.2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL, limits = c(-1.6, 1.2),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(-7, 0, 1), size = 0.3, linetype = 2, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(-7, 0, 1), color = "grey30", skip = 1, stroke = 0.2) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

```{r q-low, warning=FALSE, fig.align="center", message=FALSE}
fcsts <- expand_grid(fcsts = c("20181121180000", "20181122000000", "20181122060000"),
                     exp = c("E4", "E5", "E6", "E7"))

@@

q[bottom_top %between% c(0, 7), .(q = mean(q), u = u[bottom_top == 1], v = v[bottom_top == 1]), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = q*1000, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 0.02, 0.002)*1000) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       limits = c(1, 19),
                       guide = guide_colorsteps(#inside = FALSE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  # geom_vector(aes(x = lon, y = lat,
  #                 dx = u, dy = v), data = function(x) x[is.cross(y, x, 8)],
  #             arrow.angle = 12, size = 0.3) +
  # scale_mag() +
  cordillera +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Low level humidity (g/Kg)",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r q-middle}

q[bottom_top %between% c(8, 12), .(q = mean(q), u = u[bottom_top == 1], v = v[bottom_top == 1]), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = q*1000, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 0.02, 0.002)*1000) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       limits = c(1, 19),
                       guide = guide_colorsteps(#inside = FALSE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  # geom_vector(aes(x = lon, y = lat,
  #                 dx = u, dy = v), data = function(x) x[is.cross(y, x, 8)],
  #             arrow.angle = 12, size = 0.3) +
  # scale_mag() +
  cordillera +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Humidity (g/Kg) 800-700 hPa",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```{r v-low}
q[bottom_top %between% c(0, 7), .(v = mean(v)), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = v, fill = stat(level_d)), proj = norargentina_lambert) +
  scale_fill_divergent_discretised(name = NULL,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(#inside = FALSE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  # geom_vector(aes(x = lon, y = lat,
  #                 dx = u, dy = v), data = function(x) x[is.cross(y, x, 8)],
  #             arrow.angle = 12, size = 0.3) +
  # scale_mag() +
  cordillera +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Low level meridional wind (m/s)",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```{r v-middle}
q[bottom_top %between% c(8, 12), .(v = mean(v)), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = v, fill = stat(level_d)), proj = norargentina_lambert) +
  scale_fill_divergent_discretised(name = NULL,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(#inside = FALSE,
                                                barwidth = 25,
                                                barheight = 0.8)) +
  # geom_vector(aes(x = lon, y = lat,
  #                 dx = u, dy = v), data = function(x) x[is.cross(y, x, 8)],
  #             arrow.angle = 12, size = 0.3) +
  # scale_mag() +
  cordillera +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "800-700 hPa meridional wind (m/s)",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

```{r}
q[date == unique(date)[1:3] & west_east %between% c(70, 180)] %>% 
  .[, .(q_mean = mean(q),
        v_mean = mean(v)), by = .(bottom_top, south_north, date, exp)] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(south_north, bottom_top)) +
  geom_contour_fill(aes(z = q_mean*1000, fill = stat(level_d))) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour(aes(z = v_mean, linetype = factor(-sign(..level..))), 
               color = "grey30", size = 0.5, binwidth = 2) +
  geom_text_contour(aes(z = v_mean), color = "grey30", stroke = 0.1, breaks = seq(-10, 6, 2)) +
  scale_linetype(guide = NULL) +
  # geom_vector(aes(x = south_north, y = bottom_top,
  #                 mag = abs(v_mean), angle = fifelse(v_mean > 0, 0, 180)),
  #             arrow.angle = 6, size = 0.2, skip.x = 10) +
  # scale_mag() +
  facet_grid(date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  labs(y =  "Sigma levels", x = "Grid points") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r}
files <- Sys.glob("/home/paola.corrales/datosmunin/EXP/E*/ANA/sondeos/*")

sondeos <- purrr::map(files, function(f){

   fread(f) %>% 
    .[, value := fifelse(variable %in% c("t", "td"), value + 273.15, value)] %>% 
    .[, launch_time := as_datetime(launch_time)]

sondeos %>% 
  .[variable == "t" & !str_detect(site, "/") & 
      exp == "E4"] %>% 
  ggplot(aes(launch_time, alt/1000)) +
  geom_point(aes(color = value), size = 0.5) +
  scale_color_distiller(palette = "YlOrRd", direction = 1) +
  # geom_contour(aes(z = value - fcst_value)) +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H%M") +
  coord_cartesian(ylim = c(0, 20), expand = c(0, 0)) +
  labs(color = "T", y = NULL, x = NULL) +
  theme_minimal() +
theme(legend.position = "bottom") +

sondeos %>% 
  .[variable == "t" & !str_detect(site, "/") & !is.na(fcst_value)] %>% 
  .[, oma := value - fcst_value] %>% 
  # melt(measure.vars = c("value", "oma"), variable.name = "var") %>%  
  ggplot(aes(launch_time, alt/1000)) +
  geom_point(aes(color = oma), size = 0.5) +
  scale_color_divergent() +
  # geom_contour(aes(z = value - fcst_value)) +
  coord_cartesian(ylim = c(0, 20), expand = c(0, 0)) +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H%M") +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  labs(color = "OmA", y = NULL, x = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom") +

  plot_layout(ncol = 2, widths = c(0.3, 0.7))
```

```{r}
sondeos %>% 
  .[variable == "td" & !str_detect(site, "/") & 
      exp == "E4"] %>% 
  ggplot(aes(launch_time, alt/1000)) +
  geom_point(aes(color = value), size = 0.5) +
  scale_color_distiller(palette = "YlOrRd", direction = 1) +
  # geom_contour(aes(z = value - fcst_value)) +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H%M") +
  coord_cartesian(ylim = c(0, 20), expand = c(0, 0)) +
  labs(color = "Td", y = NULL, x = NULL) +
  theme_minimal() +
theme(legend.position = "bottom") +

sondeos %>% 
  .[variable == "td" & !str_detect(site, "/") & !is.na(fcst_value)] %>% 
  .[, oma := value - fcst_value] %>% 
  # melt(measure.vars = c("value", "oma"), variable.name = "var") %>%  
  ggplot(aes(launch_time, alt/1000)) +
  geom_point(aes(color = oma), size = 0.5) +
  scale_color_divergent() +
  # geom_contour(aes(z = value - fcst_value)) +
  coord_cartesian(ylim = c(0, 20), expand = c(0, 0)) +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H%M") +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  labs(color = "OmA", y = NULL, x = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom") +

  plot_layout(ncol = 2, widths = c(0.3, 0.7))
```

```{r}
sondeos %>% 
  .[variable == "v" & !str_detect(site, "/") & 
      exp == "E4"] %>% 
  ggplot(aes(launch_time, alt/1000)) +
  geom_point(aes(color = value), size = 0.5) +
  scale_color_divergent() +
  # geom_contour(aes(z = value - fcst_value)) +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H%M") +
  coord_cartesian(ylim = c(0, 20), expand = c(0, 0)) +
  labs(color = "V (m/s)", y = NULL, x = NULL) +
  theme_minimal() +
theme(legend.position = "bottom") +

sondeos %>% 
  .[variable == "v" & !str_detect(site, "/") & !is.na(fcst_value)] %>% 
  .[, oma := value - fcst_value] %>% 
  # melt(measure.vars = c("value", "oma"), variable.name = "var") %>%  
  ggplot(aes(launch_time, alt/1000)) +
  geom_point(aes(color = oma), size = 0.5) +
  scale_color_divergent() +
  # geom_contour(aes(z = value - fcst_value)) +
  coord_cartesian(ylim = c(0, 20), expand = c(0, 0)) +
  scale_x_datetime(date_breaks = "12 hours", date_labels = "%b %d \n %H%M") +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  labs(color = "OmA", y = NULL, x = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom") +

  plot_layout(ncol = 2, widths = c(0.3, 0.7))
```
